---
title: "Test_recoding"
author: "Luc"
date: "Friday, June 03, 2016"
output: html_document
---
---
title: "Test_recoding"
author: "Luc"
date: "Friday, June 03, 2016"
output: html_document
---
I'm trying to write a for loop for recoding several variables with the same value structure. However,it doesn't seem to work as I want it to work. 

Making a test database:
```{r}
oldname1 <- c("yes","yes","yes","no","no","no",NA)
oldname2 <- c("yes", "no","yes", "no","yes", "no",NA)
data <- data.frame(oldname1,oldname2)
data
```

List with vectors including the old name and the new name for the recoded variable:
```{r}
names <- list(c("oldname1","newname1"),c("oldname2","newname2"))
```

for loop for the recoding:
```{r}
for(name in names){
  data[name[2]]<- ifelse(data[name[1]] == "yes", 1, ifelse(data[name[1]]=="no",0,NA))
}
```

But now something strange happens with the colomn names:
```{r}
data

names(data)

summary(data)

rm(data)
```

I don't understand why this is happening and how I can fix this?

I would like to this to be the end result:
```{r message=FALSE}
library(dplyr)
oldname1 <- c("yes","yes","yes","no","no","no",NA)
oldname2 <- c("yes", "no","yes", "no","yes", "no",NA)
data <- data.frame(oldname1,oldname2)


data1 <- data %>% mutate(newname1= ifelse(oldname1=="yes",1,ifelse(oldname1=="no",0,NA)),
                         newname2= ifelse(oldname2=="yes",1,ifelse(oldname2=="no",0,NA)))


data1
names(data1)
summary(data1)
```

I like to loop solution more as this saves a lot of time if I have to recode a lot of variables that have the same value structure.And I also think the code is much cleaner and less prone for errors. But the inconsistency of the names worries me a bit.














